Type-Safe Modular Parsing

### 2017-01-12 paper/sections/Discussion.tex
Rewrite 5.3

\subsection{Alternative Techniques}
In the previous sections we have talked about Packrat Parsing, inheritance and Object Algebras. These components fuse together in our library implementation, for building extensible parsers. We want to argue here that those aspects are totally orthogonal, and hence can have their alternatives.

For example, we have conducted some previous experiments of modular paring on the Haskell language, based on open recursion, MRM [] and Parsec. \haoyuan{I mention our previous work here. } The delegation-based open recursion can be an alternative for inheritance. It exposes recursion explicitly by a parameter for ``self-reference''.
Furthermore, there has been a lot of related work that realizes extensible data types in functional programming, including MRM using a list of functors. We used Parsec as the parsing library, but suffered from the issues already illustrated in Section~\ref{subsec:challenges}. As a workaround, we made use of state monad in Parsec to ensure that a left-recursive production rule will not be applied successively in parsing. Whereas a better
parsing library would potentially introduce a lot of fancy features and parser combinators, run with high efficiency, or even support indirect left-recursion.

>>>>

\subsection{Alternative Techniques}
Under our modular parsing framework, we use Packrat parsing as the underlying parsing technique, OO inheritance with method overriding for composing and extending parsers, and Object Algebras for parsing extensible ASTs. However, our framework is more general and thus more powerful, because those aspects are orthogonal to each other, and hence can have their alternatives.

\begin{itemize}

\item {\bf Parsing Technique}

Our approach does not depend on a particular parser combinator library or parsing algorithm. We demonstrated that Packrat parsing has some advantages and is suitable in a modular setting. However, under certain circumstances or in other programming languages, it may not be the best choice. One can use other parser combinator libraries as long as it meets his requirements.

\item {\bf Composing and Extending Parsers}

We use traits to model parsers, OO inheritance to compose them, and method overriding for their extensibility. These language features may not be supported in other programming languages, especially in functional languages such as Haskell. Nevertheless, \textit{open recursion} could be used as an alternative. An explict ``self-reference'' parameter is able to explain the recursive calls dynamically, by the real argument passed at runtime.

\item {\bf Extensible ASTs}

Besides Object Algebras, many other techniques including \textit{Data types à la carte} (DTC) [] and \textit{Modular reifiable matching} (MRM) [] also support extensible data structures. These alternatives can also be adopted to build ASTs and corresponding parsers.

\end{itemize}

As we demonstrated, the whole modular parsing framework itself is modular, which means it can be customized easily. Actually, we conducted some previous experiments of modular paring in Haskell, based on open recursion, MRM and Parsec. However, we suffered from issues of Parsec, as illustrated in Section~\ref{subsec:challenges}.
